---
title: "Extraction of genotypes per fam ID"
author: "June Ro"
date: "5/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager" , repos = 'http://cran.us.r-project.org')

#BiocManager::install("RVS")

#install.packages("gRbase")
library("RVS")
library(dplyr)

```

```{r}
getwd()
setwd("/Users/junero/Desktop/BIOL/BIOL 499R /EpilepsyResearch")
fam <- read.table("/Users/junero/Desktop/BIOL/BIOL 499R /EpilepsyResearch/epi4k_exome_ped_file_forRVS.fam")
colnames(fam) <- as.character(fam[1,])
fam <- fam[-1, ]
```

```{r}
#install.packages("Matrix", repos = "http://cran.us.r-project.org")
library(Matrix)
#install.packages("kinship2", repos = "http://cran.us.r-project.org")
library(kinship2)


fam$SEX <- as.numeric(fam$SEX) #there is an error with 'sex' variable because it is a character; convert it to numeric
class(fam$SEX) #check
fam$Affected <- as.numeric(fam$Affected)
class(fam$Affected) #check


pedRVS <- pedigree(id = fam$IID, dadid = fam$PID, momid = fam$MID, sex = fam$SEX, affected = fam$Affected, famid = fam$FID, missid = 0)
fams <- unique(fam$FID)
#fams
#pedRVS

#pdf("/Users/junero/Desktop/BIOL/BIOL 499R /EpilepsyResearch/pedigrees_RVS_051421.pdf")
#for(i in 1:length(fams)){plot(pedRVS[fams[i]])legend("topleft", legend = fams[i], bty = "n")}
#dev.off() #dev. off shuts down the specified (by default the current) device. If the current device is shut down and any other devices are open, the next open device is made current.

```

```{r}
#take note of families with probability under 0.05
#for (i in 1:155){sharingprob <- RVsharing(pedRVS[fams[i]], useAffected = TRUE)print(sharingprob[which(sharingprob < 0.05)])}

#subset families with probability under 0.05
fams_under0.05 <- data.frame(famID = fams[c(5, 7, 10, 18, 21, 24, 31, 36, 42, 43, 46, 47, 54:58, 61, 71:74, 77, 79, 83, 91, 97, 100, 104, 106:109, 115, 117:120, 122, 123, 125, 129, 131, 133, 138, 140:143, 148, 149, 152)])

#fams_under0.05
```


```{r}
#install.packages("vcfR")
library(vcfR)

samID_to_gwasID <- read.table("/Users/junero/Desktop/BIOL/BIOL 499R /EpilepsyResearch/exome_sampleid_to_gwasid.txt")
#samID_to_gwasID

merged <- merge(fams_under0.05, samID_to_gwasID, by.x = "famID", by.y = "V3") 
#merged

tier2_0.01 <- read.vcfR("/Users/junero/Desktop/BIOL/BIOL 499R /EpilepsyResearch/epi4k_exome_RVS_genotypes_MAF0.01_tier2.recode.vcf", verbose = FALSE )
#head(tier2_0.01, 40)

tier1_0.01 <- read.vcfR("/Users/junero/Desktop/BIOL/BIOL 499R /EpilepsyResearch/epi4k_exome_RVS_genotypes_MAF0.01_tier1.recode.vcf", verbose = FALSE )

options(max.print=999999)
gt <- extract.gt(tier2_0.01, element = 'GT')
gt <- data.frame(gt)
```

# Extract genotype per fam ID

## famID 129
```{r}
gt_121 <- gt %>%
  select(epifam16922cgb4, epifam16028cgb1) %>%
  filter((epifam16922cgb4 == "1/1" | epifam16922cgb4 == "0/1") & (epifam16028cgb1 == "1/1" | epifam16028cgb1 == "0/1"))
gt_121
```

## famID 164
```{r}
gt_164 <- gt %>%
  select(epifam22168cgg11, epifam16790cgg1, epifam16793cgg4, epifam16795cgg6 ) %>%
  filter(epifam22168cgg11 == "1/1" | epifam22168cgg11 == "0/1" | epifam16790cgg1 == "1/1" | epifam16790cgg1 == "0/1" | epifam16793cgg4 == "1/1" | epifam16793cgg4 == "0/1" | epifam16795cgg6 == "1/1" | epifam16795cgg6 == "0/1" )
gt_164
```

## famID 165
```{r}
gt_165 <- gt %>%
  select(epifam16933blb8, epifam16799blb4, epifam16934blb9) %>%
  filter(epifam16933blb8 == "1/1" | epifam16933blb8 == "0/1" | epifam16799blb4 == "1/1" | epifam16799blb4 == "0/1" | epifam16934blb9 == "1/1" | epifam16934blb9 == "0/1")
gt_165
```

## famID 209
```{r}
gt_209 <- gt %>%
  select(epifam18396blh4, epifam18397blh1, epifam18401blh6 ) %>%
  filter(epifam18396blh4 == "1/1" | epifam18396blh4 == "0/1" | epifam18397blh1 == "1/1" | epifam18397blh1 == "0/1" | epifam18401blh6 == "1/1" | epifam18401blh6 == "0/1")
gt_209
```

## famID 280
```{r}
gt_280 <- gt %>%
  select(epifam21801cgm1, epifam22185cgm6) %>%
  filter(epifam21801cgm1 == "1/1" | epifam21801cgm1 == "0/1" | epifam22185cgm6 == "1/1" | epifam22185cgm6 == "0/1")
gt_280
```

## famID 38
```{r}
#'epifam3822btp' not found so excluded

gt_38 <- gt %>%
  select(epifam3837btp, epifam3825btp) %>%
  filter(epifam3837btp == "1/1" | epifam3837btp == "0/1" | epifam3825btp == "1/1" | epifam3825btp == "0/1")
gt_38
```

## famID 44
```{r}
gt_44 <- gt %>%
  select(epifam549biv1, epifam553biv7, epifam552biv6 ) %>%
  filter(epifam549biv1 == "1/1" | epifam549biv1 == "0/1" | epifam553biv7 == "1/1" | epifam553biv7 == "0/1" | epifam552biv6 == "1/1" | epifam552biv6 == "0/1")
gt_44
```

## famID 48
```{r}
gt_48 <- gt %>%
  select(epifam568biw1new, 	epifam576biw8) %>%
  filter(	epifam568biw1new == "1/1" | 	epifam568biw1new == "0/1" | epifam576biw8 == "1/1" | 	epifam576biw8 == "0/1")
gt_48

```

## famID 58
```{r}
gt_58 <- gt %>%
  select(epifam615bkw5, epifam614bkw1) %>%
  filter(epifam615bkw5 == "1/1" | 	epifam615bkw5 == "0/1" | epifam614bkw1 == "1/1" | epifam614bkw1 == "0/1")
gt_58
```

## famID 60
```{r}
gt_60 <- gt %>%
  select(epifam6045bts, epifam6058bts) %>%
  filter(epifam6045bts == "1/1" | 	epifam6045bts == "0/1" | epifam6058bts == "1/1" | epifam6058bts == "0/1")
gt_60
```

## famID 68
```{r}
gt_68 <- gt %>%
  select(epifam16089bix1, epifam3257bix8, epifam3261bix9) %>%
  filter(epifam16089bix1 == "1/1" | epifam16089bix1 == "0/1" | epifam3257bix8 == "1/1" | epifam3257bix8 == "0/1" | 	epifam3261bix9 == "1/1" |	epifam3261bix9 == "0/1")
gt_68
```

## famID 73
```{r}
gt_73 <- gt %>%
  select(epifam73416btt, 	epifam73414btt, epifam7329btt, epifam73314btt) %>%
  filter(epifam73416btt == "1/1" | epifam73416btt == "0/1" | 	epifam73414btt == "1/1" | 	epifam73414btt == "0/1" | epifam7329btt == "1/1" | epifam7329btt == "0/1" | epifam73314btt == "1/1" | epifam73314btt == "0/1" )
gt_73
```

## famID 80388
```{r}
gt_80388 <- gt %>%
  select(epifam5669cgp12, epifam5660cgp1, epifam6870cgp14) %>%
  filter(epifam5669cgp12 == "1/1" | epifam5669cgp12 == "0/1" | epifam5660cgp1 == "1/1" | epifam5660cgp1 == "0/1" | 	epifam6870cgp14 == "1/1" |	epifam6870cgp14 == "0/1")
gt_80388
```

## famID 81081
```{r}
gt_81081 <- gt %>%
  select(epifam2001cgu5, epifam23269cgu7, epifam8246cgu1) %>%
  filter(epifam2001cgu5 == "1/1" | epifam2001cgu5 == "0/1" | epifam23269cgu7 == "1/1" | epifam23269cgu7 == "0/1" | 	epifam8246cgu1 == "1/1" |	epifam8246cgu1 == "0/1")
gt_81081
```

## famID 81397
```{r}
gt_81397 <- gt %>%
  select(epifam8862cgx3, epifam26635cgx5, epifam26092cgx1 ) %>%
  filter(epifam8862cgx3 == "1/1" | epifam8862cgx3 == "0/1" | epifam26635cgx5 == "1/1" | epifam26635cgx5 == "0/1" | 	epifam26092cgx1 == "1/1" |	epifam26092cgx1 == "0/1")
gt_81397
```

## famID 82036
```{r}
gt_82036 <- gt %>%
  select(epifam10021chc4, epifam10075chc6, epifam9514chc1 ) %>%
  filter(epifam10021chc4 == "1/1" | epifam10021chc4 == "0/1" | epifam10075chc6 == "1/1" | epifam10075chc6 == "0/1" | 	epifam9514chc1 == "1/1" |	epifam9514chc1 == "0/1")
gt_82036
```

## famID 82065
```{r}
gt_82065 <- gt %>%
  select(epifam14543bme8, epifam14104bme1, epifam14103bme4) %>%
  filter(epifam14543bme8 == "1/1" | epifam14543bme8 == "0/1" | epifam14104bme1 == "1/1" | epifam14104bme1 == "0/1" | 	epifam14103bme4 == "1/1" |	epifam14103bme4 == "0/1")
gt_82065
```

## famID 82072
```{r}
gt_82072 <- gt %>%
  select(epifam14735beb7, epifam14766beb5, epifam15430beb1) %>%
  filter(epifam14735beb7 == "1/1" | epifam14735beb7 == "0/1" | 	epifam14766beb5 == "1/1" | 	epifam14766beb5 == "0/1" | 	epifam15430beb1 == "1/1" |	epifam15430beb1 == "0/1")
gt_82072
```

## famID 82427
```{r}
#'epifam204che4' not found so excluded

gt_82427 <- gt %>%
  select(epifam224che6, epifam248che1) %>%
  filter(epifam224che6 == "1/1" | epifam224che6 == "0/1" | 	epifam248che1 == "1/1" | 	epifam248che1 == "0/1")
gt_82427
```

## famID 82451_EPGP014255
```{r}
gt_82451_EPGP014255 <- gt %>%
  select(epifam701ach8, epifam868ach10) %>%
  filter(epifam701ach8 == "1/1" | epifam701ach8 == "0/1" | 	epifam868ach10 == "1/1" | 	epifam868ach10 == "0/1")
gt_82451_EPGP014255
```

## famID 82467
```{r}
gt_82467<- gt %>%
  select(epifam744chf5, epifam293chf1, epifam723chf4 ) %>%
  filter(epifam744chf5 == "1/1" | epifam744chf5 == "0/1" | 	epifam293chf1 == "1/1" | epifam293chf1 == "0/1" | 	epifam723chf4 == "1/1" |	epifam723chf4 == "0/1")
gt_82467
```

## famID 82470
```{r}
gt_82470<- gt %>%
  select(epifam302chg5, epifam2361chg4, epifam1204chg1) %>%
  filter(epifam302chg5 == "1/1" | epifam302chg5 == "0/1" | epifam2361chg4 == "1/1" | epifam2361chg4 == "0/1" | 	epifam1204chg1 == "1/1" |	epifam1204chg1 == "0/1")
gt_82470
```

## famID 82472
```{r}
gt_82472 <- gt %>%
  select(epifam703chh6, epifam312chh1) %>%
  filter(epifam703chh6 == "1/1" | epifam703chh6 == "0/1" | 	epifam312chh1 == "1/1" | 	epifam312chh1 == "0/1")
gt_82472
```

## famID 82522
```{r}
gt_82522<- gt %>%
  select(epifam791chj1, epifam794chj4, epifam792chj2) %>%
  filter(epifam791chj1 == "1/1" | epifam791chj1 == "0/1" | epifam794chj4 == "1/1" | epifam794chj4 == "0/1" | 	epifam792chj2 == "1/1" |	epifam792chj2 == "0/1")
gt_82522
```

## famID 82549
```{r}
gt_82549<- gt %>%
  select(epifam16847chm1, epifam943chm9, epifam877chm6) %>%
  filter(epifam16847chm1 == "1/1" | epifam16847chm1 == "0/1" | epifam943chm9 == "1/1" | epifam943chm9 == "0/1" | 	epifam877chm6 == "1/1" |	epifam877chm6 == "0/1")
gt_82549
```

## famID 82692
```{r}
#'epifam1480chs11' not found so excluded
gt_82692 <- gt %>%
  select(epifam1571chs3, 	epifam32136chs13, epifam1422chs9, epifam73314btt) %>%
  filter(epifam1571chs3 == "1/1" | epifam1571chs3 == "0/1" | 	epifam32136chs13 == "1/1" | epifam32136chs13 == "0/1" | epifam1422chs9 == "1/1" | epifam1422chs9 == "0/1")
gt_82692
```

## famID 83383
```{r}
gt_83383 <- gt %>%
  select(epifam2955cia1, epifam3087cia4, epifam3757cia8) %>%
  filter(epifam2955cia1 == "1/1" | epifam2955cia1 == "0/1" | 	epifam3087cia4 == "1/1" | epifam3087cia4 == "0/1" | epifam3757cia8 == "1/1" | epifam3757cia8 == "0/1")
gt_83383
```

## famID 83438
```{r}
gt_83438 <- gt %>%
  select(epifam3352ckc1, epifam3623ckc9) %>%
  filter(epifam3352ckc1 == "1/1" | 	epifam3352ckc1 == "0/1" | epifam3623ckc9 == "1/1" | epifam3623ckc9 == "0/1")
gt_83438
```

## famID 83506
```{r}
gt_83506 <- gt %>%
  select(epifam3786cic1, epifam3788cic8, epifam17077cic5) %>%
  filter(epifam3786cic1 == "1/1" | epifam3786cic1 == "0/1" | 	epifam3788cic8 == "1/1" | epifam3788cic8 == "0/1" | epifam17077cic5 == "1/1" | epifam17077cic5 == "0/1")
gt_83506
```

## famID 83787
```{r}
gt_83787 <- gt %>%
  select(epifam16707cif1, epifam18860cif18, epifam17407cif9, epifam17405cif8) %>%
  filter(epifam16707cif1 == "1/1" | epifam16707cif1 == "0/1" | 	epifam18860cif18 == "1/1" | 	epifam18860cif18 == "0/1" | 	epifam17407cif9 == "1/1" | 	epifam17407cif9 == "0/1" | epifam17405cif8 == "1/1" | epifam17405cif8 == "0/1" )
gt_83787
```

## famID 83795
```{r}
gt_83795 <- gt %>%
  select(epifam23876ckd7, epifam24310ckd8, epifam16718ckd1) %>%
  filter(epifam23876ckd7 == "1/1" | epifam23876ckd7 == "0/1" | 	epifam24310ckd8 == "1/1" | 	epifam24310ckd8 == "0/1" | epifam16718ckd1 == "1/1" | epifam16718ckd1 == "0/1")
gt_83795
```

## famID 84033
```{r}
gt_84033 <- gt %>%
  select(epifam17514bmf7, epifam15207bmf1) %>%
  filter(epifam17514bmf7 == "1/1" | epifam17514bmf7 == "0/1" | epifam15207bmf1 == "1/1" | epifam15207bmf1 == "0/1")
gt_84033
```

## famID 84584_EPGP012661
```{r}
gt_84584_EPGP012661 <- gt %>%
  select(epprnd31238anz1, epifam20726anz8) %>%
  filter(epprnd31238anz1 == "1/1" | epprnd31238anz1 == "0/1" | epifam20726anz8 == "1/1" | epifam20726anz8 == "0/1")
gt_84584_EPGP012661
```

## famID 84762_EPGP015319
```{r}
gt_84762_EPGP015319 <- gt %>%
  select(epifam20618ayz6, epifam21504ayz10, epprnd37465ayz1, epifam21279ayz8, epifam20510ayz5) %>%
  filter(epifam20618ayz6 == "1/1" | epifam20618ayz6 == "0/1" | 	epifam21504ayz10 == "1/1" | 	epifam21504ayz10 == "0/1" | epprnd37465ayz1 == "1/1" | 	epprnd37465ayz1 == "0/1" | epifam21279ayz8 == "1/1" | epifam21279ayz8 == "0/1" | epifam20510ayz5 == "1/1" | epifam20510ayz5 == "0/1" )
gt_84762_EPGP015319
```

## famID 84832
```{r}
gt_84832 <- gt %>%
  select(epifam19737cil7, 	epifam19189cil1) %>%
  filter(epifam19737cil7 == "1/1" | epifam19737cil7 == "0/1" | 	epifam19189cil1 == "1/1" |	epifam19189cil1 == "0/1")
gt_84832
```

## famID 84834
```{r}
gt_84834 <- gt %>%
  select(epifam19193cim1, epifam20443cim4, epifam26630cim8) %>%
  filter(	epifam19193cim1 == "1/1" | 	epifam19193cim1 == "0/1" | 	epifam20443cim4 == "1/1" | 	epifam20443cim4 == "0/1" | epifam26630cim8 == "1/1" | epifam26630cim8 == "0/1")
gt_84834
```

## famID 84858
```{r}
#Column `epifam19249cio4` and epifam19248cio3 doesn't exist so excluded

gt_84858 <- gt %>%
  select(epifam19250cio5, epifam19246cio1, epifam24027cio7) %>%
  filter(epifam19250cio5 == "1/1" | 	epifam19250cio5 == "0/1" | epifam19246cio1 == "1/1" | 	epifam19246cio1 == "0/1" | epifam24027cio7 == "1/1" | epifam24027cio7 == "0/1" )
gt_84858
```

## famID 86269
```{r}
gt_86269 <- gt %>%
  select(epifam23043ckg6, 	epifam23807ckg5, epifam23046ckg1) %>%
  filter(	epifam23043ckg6 == "1/1" | 	epifam23043ckg6 == "0/1" | 		epifam23807ckg5 == "1/1" | 		epifam23807ckg5 == "0/1" | epifam23046ckg1 == "1/1" | epifam23046ckg1 == "0/1")
gt_86269
```

## famID 87223
```{r}
gt_87223 <- gt %>%
  select(epifam3875cjg18, epifam25608cjg1) %>%
  filter(epifam3875cjg18 == "1/1" | epifam3875cjg18 == "0/1" | 	epifam25608cjg1 == "1/1" | epifam25608cjg1 == "0/1")
```

## famID 87246
```{r}
gt_87246 <- gt %>%
  select(	epifam26253cjh7, epifam25690cjh4, epifam25686cjh1) %>%
  filter(	epifam26253cjh7 == "1/1" | 		epifam26253cjh7 == "0/1" | 	epifam25690cjh4 == "1/1" | 	epifam25690cjh4 == "0/1" | epifam25686cjh1 == "1/1" | epifam25686cjh1 == "0/1")
gt_87246
```

## famID 87711
```{r}
gt_87711 <- gt %>%
  select(	epifam31968cjk3, epifam31966cjk1, epifam26915cjk5) %>%
  filter(	epifam31968cjk3 == "1/1" | 	epifam31968cjk3 == "0/1" | 	epifam31966cjk1 == "1/1" | 	epifam31966cjk1 == "0/1" | epifam26915cjk5 == "1/1" | epifam26915cjk5 == "0/1")
gt_87711

```

## famID 88
```{r}
gt_88 <- gt %>%
  select(epifam8832btw, epifam8835btw, epifam8828btw) %>%
  filter(epifam8832btw == "1/1" | epifam8832btw == "0/1" | epifam8835btw == "1/1" | epifam8835btw == "0/1" | epifam8828btw == "1/1" | epifam8828btw == "0/1")
gt_88
```

## famID 90022
```{r}
gt_90022 <- gt %>%
  select(epifam20166bml21, epifam20689bml6, epifam20224bml2) %>%
  filter(epifam20166bml21 == "1/1" | epifam20166bml21 == "0/1" | epifam20689bml6 == "1/1" | epifam20689bml6 == "0/1" | epifam20224bml2 == "1/1" | epifam20224bml2 == "0/1")
gt_90022
```

## famID A
```{r}
gt_A <- gt %>%
  select(epifam01228bin13, 	epifam01223bin9, epifam01232bin7 ) %>%
  filter(epifam01228bin13 == "1/1" | epifam01228bin13 == "0/1" | 	epifam01223bin9 == "1/1" | 	epifam01223bin9 == "0/1" | epifam01232bin7 == "1/1" | epifam01232bin7 == "0/1")
gt_A
```

## famID EG29
```{r}
gt_EG29 <- gt %>%
  select(epifam2912ckp3, epifam2911ckp1, epifam2902ckp2 ) %>%
  filter(epifam2912ckp3 == "1/1" | epifam2912ckp3 == "0/1" | 	epifam2911ckp1 == "1/1" | 	epifam2911ckp1 == "0/1" | epifam2902ckp2 == "1/1" | epifam2902ckp2 == "0/1")
gt_EG29
```

## famID EG302
```{r}
gt_EG302 <- gt %>%
  select(epifam30201bjk1, epifam30207bjk7, 	epifam30204bjk4 ) %>%
  filter(epifam30201bjk1 == "1/1" | epifam30201bjk1 == "0/1" | epifam30207bjk7 == "1/1" | epifam30207bjk7 == "0/1" | 	epifam30204bjk4 == "1/1" | 	epifam30204bjk4 == "0/1")
gt_EG302
```

## famID EG44
```{r}
gt_EG44 <- gt %>%
  select(epifam4417ckq2, epifam4419ckq3, epifam4401ckq1 ) %>%
  filter(epifam4417ckq2 == "1/1" | 	epifam4417ckq2 == "0/1" | epifam4419ckq3 == "1/1" | epifam4419ckq3 == "0/1" | epifam4401ckq1 == "1/1" | epifam4401ckq1 == "0/1")
gt_EG44
```

## famID EG46
```{r}
gt_EG46 <- gt %>%
  select(epifam4602ckr1, epifam4625ckr2) %>%
  filter(epifam4602ckr1 == "1/1" | epifam4602ckr1 == "0/1" | epifam4625ckr2 == "1/1" | epifam4625ckr2 == "0/1")
gt_EG46
```

## famID EG60
```{r}
gt_EG60 <- gt %>%
  select(epifam6006bje6, epifam6001bje1, epifam6004bje4) %>%
  filter(epifam6006bje6 == "1/1" | 	epifam6006bje6 == "0/1" | epifam6001bje1 == "1/1" | epifam6001bje1 == "0/1" | epifam6004bje4 == "1/1" | epifam6004bje4 == "0/1")
gt_EG60
```

## famID EP13
```{r}
gt_EP13 <- gt %>%
  select(	epifam139cky3, epifam141cky4, 	epifam132cky2) %>%
  filter(	epifam139cky3 == "1/1" | 		epifam139cky3 == "0/1" | epifam141cky4 == "1/1" | epifam141cky4 == "0/1" | 	epifam132cky2 == "1/1" | 	epifam132cky2 == "0/1")
gt_EP13
```

## famID EP236
```{r}
gt_EP236 <- gt %>%
  select(	epifam2362cla1, epifam2361cla2, epifam2363cla3) %>%
  filter(	epifam2362cla1 == "1/1" | 	epifam2362cla1 == "0/1" | epifam2361cla2 == "1/1" | epifam2361cla2 == "0/1" | epifam2363cla3 == "1/1" | epifam2363cla3 == "0/1")
gt_EP236
```

## famID EP26
```{r}
gt_EP26 <- gt %>%
  select(epifam2624ckv3, epifam2616ckv1, epifam2604ckv2) %>%
  filter(epifam2624ckv3 == "1/1" | 	epifam2624ckv3 == "0/1" | epifam2616ckv1 == "1/1" | epifam2616ckv1 == "0/1" | epifam2604ckv2 == "1/1" | epifam2604ckv2 == "0/1")
gt_EP26
```

```{r}
#visualization
#heatmap.bp(gt)

chrom <- create.chromR(name='Supercontig', vcf=tier2_0.01)
chrom <- proc.chromR(chrom, verbose=TRUE)
plot(chrom)
chromoqc(chrom, dp.alpha=20)
```



