---
title: "Project"
author: "June Ro"
date: "11/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("/Users/cathystout/Desktop/QTM 151")
getwd()
data <- read.csv("county_deaths_prop_column.csv") #Import data
data

library(dplyr)
library(tidyverse)
library(ggplot2)

top_3 <- data %>% 
  group_by(State) %>% 
  summarise(average_prop_covid = mean(prop_covid)) %>% 
  arrange(desc(average_prop_covid)) %>% 
  head(3)

top_3 #top 3 states with the highest covid deaths are NJ, ND and DC


bottom_3 <- data %>% 
  group_by(State) %>% 
  summarise(average_prop_covid = mean(prop_covid)) %>% 
  arrange(desc(average_prop_covid)) %>% 
  tail(3)

bottom_3 #bottom 3 states with the lowest covid deaths are ME, OR and HI

top_bottom <- rbind(top_3, bottom_3)

top_bottom

top_bottom %>%
ggplot(aes(reorder(State, -average_prop_covid), average_prop_covid)) +
  geom_bar(aes(fill=State), stat="identity") +
  labs(x="State", y="Mean Proportion of Covid Deaths", title="Top 3 and Bottom 3 States for Covid Death Rates")
```

```{r}


#############THIS PART IS FOR VISUALIZATION, MOVE ON WITHOUT RUNNING THIS PART1#############
install.packages("maps")
library(maps)
install.packages("ggmap")
library(ggmap)

long_lat_data <- read.csv("test.csv")
long_lat_data

county_df <- map_data("county") %>%
    filter(region == "new jersey")
county_df
state_df <- map_data("state")%>%
    filter(region == "new jersey")
state_df



states <- map_data("state")
nj_df <- states %>%
  filter(region == "new jersey")
nj_df

nj_base <- ggplot(data = nj_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_quickmap() + 
  geom_polygon(color = "black", fill = "pink")

nj_base + theme_void() + 
  geom_polygon(data = county_df, aes(x=long, y=lat, group=group),fill = NA, color = "white") +
  geom_polygon(data=state_df, color = "black", fill = NA) 

```


New Jersey viz
```{r}
county_df <- map_data("county") %>%
    filter(region == "new jersey")
county_df
state_df <- map_data("state")%>%
    filter(region == "new jersey")
state_df

nj_data <- data %>% filter(State == "NJ") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
nj_data$County <- tolower(nj_data$County)
nj_data

mapdat <- left_join(nj_data, county_df, by = c("County"="subregion"))
mapdat %>% filter(County=="cape")
nj_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
nj_lat_long
mapdat %>% filter(County == "union")

 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill="blue", colour = "white") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="blue"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=nj_lat_long, aes(long, lat, label = County, size=I(2.5))) + geom_text(aes(x=-74.8, y=39.2, label = "cape", alpha=I(0.01), size=I(2.5)))
 
```


Maine viz
```{r}
county_df <- map_data("county") %>%
    filter(region == "maine")
county_df
state_df <- map_data("state")%>%
    filter(region == "maine")
state_df

data
maine_data <- data %>% filter(State == "ME") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
maine_data$County <- tolower(maine_data$County)
maine_data

mapdat <- left_join(maine_data, county_df, by = c("County"="subregion"))

maine_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
maine_lat_long


 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill="gray", colour = "white") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="white"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=maine_lat_long, aes(long, lat, label = County, size=I(2.5))) 
```

Oregon viz
```{r}
county_df <- map_data("county") %>%
    filter(region == "oregon")
county_df
state_df <- map_data("state")%>%
    filter(region == "oregon")
state_df

data
or_data <- data %>% filter(State == "OR") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
or_data$County <- tolower(or_data$County)
or_data

mapdat <- left_join(or_data, county_df, by = c("County"="subregion"))

or_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
or_lat_long


 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill="gray", colour = "white") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="white"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=or_lat_long, aes(long, lat, label = County, size=I(2.5))) 
```

```{r}
county_df <- map_data("county") %>%
    filter(region == "new york")
county_df
state_df <- map_data("state")%>%
    filter(region == "new york")
state_df

data
ny_data <- data %>% filter(State == "NY") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
ny_data$County <- tolower(ny_data$County)
ny_data

mapdat <- left_join(ny_data, county_df, by = c("County"="subregion"))

ny_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
ny_lat_long


 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill="gray", colour = "white") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="white"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=ny_lat_long, aes(long, lat, label = County, size=I(2.5))) 
```


```{r}
county_df <- map_data("county") %>%
    filter(region == "georgia")
county_df
state_df <- map_data("state")%>%
    filter(region == "georgia")
state_df

data
ga_data <- data %>% filter(State == "GA") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
ga_data$County <- tolower(ga_data$County)
ga_data

mapdat <- left_join(ga_data, county_df, by = c("County"="subregion"))

ga_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
ga_lat_long


 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill="gray", colour = "white") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="white"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=ga_lat_long, aes(long, lat, label = County, size=I(2.5))) 
```
```{r}
county_df <- map_data("county") %>%
    filter(region == "california")
county_df
state_df <- map_data("state")%>%
    filter(region == "california")
state_df

data
ca_data <- data %>% filter(State == "CA") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
ca_data$County <- tolower(ca_data$County)
ca_data

mapdat <- left_join(ca_data, county_df, by = c("County"="subregion"))

ca_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
ca_lat_long


 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill="gray", colour = "white") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="white"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=ca_lat_long, aes(long, lat, label = County, size=I(2.5))) 
```
```{r}
county_df <- map_data("county") %>%
    filter(region == "florida")
county_df
state_df <- map_data("state")%>%
    filter(region == "florida")
state_df

data
fl_data <- data %>% filter(State == "FL") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
fl_data$County <- tolower(fl_data$County)
fl_data

mapdat <- left_join(fl_data, county_df, by = c("County"="subregion"))

fl_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
fl_lat_long


 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill="pink", colour = "white") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="white"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=fl_lat_long, aes(long, lat, label = County, size=I(2.5))) 
```
```{r}
county_df <- map_data("county") %>%
    filter(region == "washington")
county_df
state_df <- map_data("state")%>%
    filter(region == "washington")
state_df

data
wa_data <- data %>% filter(State == "WA") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
wa_data$County <- tolower(wa_data$County)
wa_data

mapdat <- left_join(wa_data, county_df, by = c("County"="subregion"))

wa_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
wa_lat_long


 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill=NA, colour = "black") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="white"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=wa_lat_long, aes(long, lat, label = County, size=I(2.5))) 
```
```{r}
county_df <- map_data("county") %>%
    filter(region == "texas")
county_df
state_df <- map_data("state")%>%
    filter(region == "texas")
state_df

data
tx_data <- data %>% filter(State == "TX") %>% separate(County.name, c("County", "test"), sep = " ") %>% select(-test)
tx_data$County <- tolower(tx_data$County)
tx_data

mapdat <- left_join(tx_data, county_df, by = c("County"="subregion"))

tx_lat_long <- mapdat %>% select(County, long, lat, prop_covid, group) %>%  group_by(County) %>% summarise(long = mean(long, na.rm=T), lat = mean(lat, na.rm=T), prop = mean(prop_covid, na.rm=T), group=mean(group, na.rm=T)) 
tx_lat_long


 ggplot(mapdat, aes(long, lat, group = group), color = "white", fill=NA) +
        geom_polygon(data = state_df, fill="gray", colour = "white") + 
        theme_void() + 
        geom_polygon(aes(fill = prop_covid, color="white"), colour = alpha("white", 1/2)) +coord_fixed(1.2) + scale_fill_gradient(low="blue", high="red") +
        geom_text(data=tx_lat_long, aes(long, lat, label = County, size=I(2.5))) 
```


Bottom: ME = Maine (lowest death due to COVID)
```{r}
Bottom_ME <- data %>% 
  filter(State =="ME") %>% 
  select("State", "County.name", "Urban.Rural.Code", "prop_covid") %>% 
  group_by(Urban.Rural.Code) %>% 
  arrange(desc(prop_covid))
  
Bottom_ME
```

Bottom: HI = Hawaii (second lowest death due to COVID)
```{r}
Bottom_HI <- data %>% 
  filter(State =="HI") %>% 
  select("State", "County.name", "Urban.Rural.Code", "prop_covid") %>% 
  group_by(Urban.Rural.Code) %>% 
  arrange(desc(prop_covid))
  
Bottom_HI
```

Bottom: OR = Oregon (third lowest death due to COVID)
```{r}
Bottom_OR <- data %>% 
  filter(State =="OR") %>% 
  select("State", "County.name", "Urban.Rural.Code", "prop_covid") %>% 
  group_by(Urban.Rural.Code) %>% 
  arrange(desc(prop_covid))
  
Bottom_OR
```



Top: NJ = New Jersey (highest death due to COVID)
```{r}
Top_NJ <- data %>% 
  filter(State =="NJ") %>% 
  select("State", "County.name", "Urban.Rural.Code", "prop_covid") %>% 
  group_by(Urban.Rural.Code) %>% 
  arrange(desc(prop_covid))
  
Top_NJ
```

Top: DC = DC Metopolitan(second highest death due to COVID)
```{r}
Top_DC <- data %>% 
  filter(State =="DC") %>% 
  select("State", "County.name", "Urban.Rural.Code", "prop_covid") %>% 
  group_by(Urban.Rural.Code) %>% 
  arrange(desc(prop_covid))
  
Top_DC
```

Top: ND = North Dakota (third highest death due to COVID)
```{r}
Top_ND <- data %>% 
  filter(State =="ND") %>% 
  select("State", "County.name", "Urban.Rural.Code", "prop_covid") %>% 
  group_by(Urban.Rural.Code) %>% 
  arrange(desc(prop_covid))
  
Top_ND
```


```{r}
data_6states <- data %>% 
  filter(State == "ME" | State == "HI" | State == "OR" | State == "ND" | State == "NJ" | State == "DC") 

data_6states
```


```{r}
#sort prop covid among 6 states for large central metro type
top_lcm <- data_6states %>% 
  filter(Urban.Rural.Code == "Large central metro") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(1)

low_lcm <- data_6states %>% 
  filter(Urban.Rural.Code == "Large central metro") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(-1)

lcm <- rbind(top_lcm, low_lcm)

lcm

#Highest prop_covid by death for a specific county for large central metro type is Hudson County in New Jersey (0.29), while lowest is Multnomah County in Oregon (0.04).
```


```{r}
#sort prop covid among 6 states for micropolitan type
top_micro <- data_6states %>% 
  filter(Urban.Rural.Code == "Micropolitan") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(1)

low_micro <- data_6states %>% 
  filter(Urban.Rural.Code == "Micropolitan") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(-1)


micro <- rbind(top_micro, low_micro)
micro

#Highest prop_covid by death per cases for a specific county for micropolitan type is McHenry County, North Dakota (0.25) , while lowest is Kennebec County in Maine (0.01).
```


```{r}
#sort prop covid among 6 states for medium metro type
top_mm <- data_6states %>% 
  filter(Urban.Rural.Code == "Medium metro") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(1)

low_mm <- data_6states %>% 
  filter(Urban.Rural.Code == "Medium metro") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(-1)

mm <- rbind(top_mm, low_mm)

mm

#Highest prop_covid by death per cases for a specific county for medium metro type is  Mercer County in New Jersey (0.20), while lowest is Lane County in Oregon (0.01).
```

```{r}
#sort prop covid among 6 states for small metro type
top_sm <- data_6states %>% 
  filter(Urban.Rural.Code == "Small metro") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(1)

low_sm <- data_6states %>% 
  filter(Urban.Rural.Code == "Small metro") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(-1)

sm <- rbind(top_sm, low_sm)

sm

#Highest prop_covid by death per cases for a specific county for small metro type is Burleigh County in North Dakota (0.11), while lowest is Jackson County in Oregon (0.005).
```

```{r}
#sort prop covid among 6 states for noncore type (but note that there are only two counties listed in noncore type)
top_nc <- data_6states %>% 
  filter(Urban.Rural.Code == "Noncore") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(1)

low_nc <- data_6states %>% 
  filter(Urban.Rural.Code == "Noncore") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(-1)

nc <- rbind(top_nc, low_nc)

nc

#Highest prop_covid by death per cases for a specific county for noncore type is Bottineau County in North Dakota (0.28), while lowest is Waldo County in Maine (0.07).
```

```{r}
#sort prop covid among 6 states for large fringe metro type
top_lfm <- data_6states %>% 
  filter(Urban.Rural.Code == "Large fringe metro") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(1)

low_lfm <- data_6states %>% 
  filter(Urban.Rural.Code == "Large fringe metro") %>% 
  arrange(desc(prop_covid)) %>% 
  top_n(-1)

lfm <- rbind(top_lfm, low_lfm)

lfm

#Highest prop_covid by death per cases for a specific county for Large fringe metro type is Passaic County in New Jersey (0.27), while the lowest is Yamhill County in Oregon (0.02).
```

Graph of Highest and Lowest Proportion of COVID-19 Deaths based on City Type   
```{r}
top_bottom <- rbind(lcm, micro, mm, sm, nc, lfm)

ggplot(data=top_bottom, aes(x=Urban.Rural.Code, y=prop_covid)) +
  geom_bar(aes(fill = State), stat="identity", position="dodge") + 
  xlab("Urban Rural Code") +
  ylab("Proportion of Total Deaths due to COVID-19") +
  ggtitle("States with the Highest Proportion of COVID-19 deaths in Individual Types of Cities")
```

State Population Density
```{r}
#Data from: https://www.statista.com/statistics/183588/population-density-in-the-federal-states-of-the-us/
state <- c("NJ", "ME", "OR", "ND")
density <- c(1207.8, 43.6, 43.9, 11)
df1 <- data.frame(state)
df2 <- data.frame(density)
state_density <- cbind(df1,df2)

ggplot(data=state_density, aes(x=state, y=density)) +
  geom_bar(aes(fill = state), stat="identity") +
  scale_y_log10() + 
  ylab("log10 density (residents/square mile)") + 
  ggtitle("Population Density by State")
```
Third slide: state mask mandates and voting for trump or biden 




