---
title: "ExploratoryResearch"
author: "June Ro"
date: "7/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
install.packages("ggplot2",repos = 'http://cran.us.r-project.org')
suppressWarnings(library(ggplot2))
install.packages("dplyr",repos = 'http://cran.us.r-project.org')
suppressWarnings(library(dplyr))
```

# Variables for dietary habits

> average consumption of water (in glasses)

```{r}
load("MIDUS.rda")
da29282.0001 <- rename(da29282.0001, water = B4H19)
table2 <- table(da29282.0001$water)
round((prop.table(table2)*100), digits=2) #percentages round up to 2 

ggplot(data = da29282.0001, aes(x = water)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "darkolivegreen3") +
  scale_y_continuous(labels=scales::percent) +
  ylab("percentage") +
  xlab("water consumption")
```

> average consumption of sugared beverages (in glasses)

```{r}
da29282.0001 <- rename(da29282.0001, sugar = B4H20)
table2 <- table(da29282.0001$sugar)
round((prop.table(table2)*100), digits=2) #percentages round up to 2 

ggplot(data = da29282.0001, aes(x = sugar)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "coral2") +
  scale_y_continuous(labels=scales::percent) +
  ylab("percentage") +
  xlab("sugared beverage consumption")

```

> average servings of fruit and vegetables

```{r}
da29282.0001 <- rename(da29282.0001, fruitsVeggies = B4H21)
table2 <- table(da29282.0001$fruitsVeggies)
round((prop.table(table2)*100), digits=2) #percentages round up to 2 

ggplot(data = da29282.0001, aes(x = fruitsVeggies)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "plum4") +
  scale_y_continuous(labels=scales::percent) +
  ylab("percentage") +
  xlab("fruits and vegetables consumption")
```

> average servings of whole grain

```{r}
da29282.0001 <- rename(da29282.0001, wholeGrain = B4H22)
table2 <- table(da29282.0001$wholeGrain)
round((prop.table(table2)*100), digits=2) #percentages round up to 2 

ggplot(data = da29282.0001, aes(x = wholeGrain)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "peachpuff3") +
  scale_y_continuous(labels=scales::percent) +
  ylab("percentage") +
  xlab("whole grain consumption")

```

> average consumption of ocean fish

```{r}
da29282.0001 <- rename(da29282.0001, fish = B4H23A)
table2 <- table(da29282.0001$fish)
round((prop.table(table2)*100), digits=2) #percentages round up to 2 

ggplot(data = da29282.0001, aes(x = fish)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "lightblue3") +
  scale_y_continuous(labels=scales::percent) +
  ylab("percentage") +
  xlab("ocean fish consumption")
```

> average consumption of lean meat

```{r}
da29282.0001 <- rename(da29282.0001, meat = B4H23C)
table2 <- table(da29282.0001$meat)
round((prop.table(table2)*100), digits=2) #percentages round up to 2 

ggplot(data = da29282.0001, aes(x = meat)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "sienna3") +
  scale_y_continuous(labels=scales::percent) +
  ylab("percentage") +
  xlab("lean meat consumption")

```

# Variables for health indicators

> blood relatives diabetes

```{r}
da29282.0001 <- rename(da29282.0001, diabetes = B4H15F)
table2 <- table(da29282.0001$diabetes)
round((prop.table(table2)*100), digits=2) #percentages round up to 2 

ggplot(data = da29282.0001, aes(x = diabetes)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "skyblue4") +
  scale_y_continuous(labels=scales::percent) +
  ylab("percentage") +
  xlab("blood relative diabetes")

```

> blood hemoglobin A1c %

```{r}
da29282.0001 <- rename(da29282.0001, hemoglobin = B4BHA1C)
summary(da29282.0001$hemoglobin)
```

> average BP diastolic

```{r}
da29282.0001 <- rename(da29282.0001, BPdiastolic = B4P1GD)
summary(da29282.0001$BPdiastolic)
```

> average BP systolic

```{r}
da29282.0001 <- rename(da29282.0001, BPsystolic = B4P1GS)
summary(da29282.0001$BPsystolic)
```



